Deriving Multi-Headed Projective Dependency Parses from Link Grammar Parses

### 2014-11-21 doc/LinksToDAG_final.tex
added introduction, edited bib, updated todonotes.sty to later version

\item The resulting parses may be useful data for evaluating new parsing {\em algorithms}.  There has been a good deal of recent research on projective dependency parsing, variously using global optimization or sequential classification. \noteJE{add citations} Some of these algorithms could be extended to the {\em multi-headed} case, which is of linguistic interest for reasons discussed below.  However, it is not clear how to evaluate such algorithms.  For training and testing, one needs a plausible sample of multi-headed planar dependency parses of real sentences.  Our method cheaply manufactures such a sample, to compensate for the lack of gold-standard data of this form.\footnote{A reasonable objection to this line of algorithmic work is that the projectivity or planarity restriction is linguistically questionable even for single-headed parsing, and even more so for multi-headed parsing.  So why not go straight to {\em non}-projective multi-headed parsing?  Mainly, because efficient algorithms often exist in the projective case, and these projective algorithms can be useful as an intermediate step in producing non-planar parses.  Since natural-language parses tend to be ``almost projective'' in practice (\cite{pitler}), one can use a fast projective parser as the first step in a coarse-to-fine or stacking architecture, in order to obtain preliminary edge scores that are supplied to a non-projective parser.  Another approach is 
``pseudo-projectivization,'' where we reversibly transform non-projective parses into a projective annotation style so that projective parsers can be used.
\noteJE{cite Pitler}}

@@

\begin{figure}[t!]
  \small
  \centering
  \includegraphics[width=0.7\textwidth, keepaspectratio=true]{figure/precision_recall.png}
  \caption{Rapid convergence to the direction mapping obtained on the largest dataset.  The direction mappings obtained on small datasets have high {\em precision} relative to the one obtained on the largest dataset.  {\em Recall} grows as more link types are seen and directionalized.}\label{fig:convergence}
  \vspace{-6pt}
\end{figure}

>>>>

\item The resulting parses may be useful data for evaluating new parsing {\em algorithms}.  There has been a good deal of recent research on projective dependency parsing, variously using global optimization or sequential classification. \noteJE{add citations} Some of these algorithms could be extended to the {\em multi-headed} case, which is of linguistic interest for reasons discussed below.  However, it is not clear how to evaluate such algorithms.  For training and testing, one needs a plausible sample of multi-headed planar dependency parses of real sentences.  Our method cheaply manufactures such a sample, to compensate for the current lack of gold-standard data of this form.\footnote{A reasonable objection to this line of algorithmic work is that the projectivity or planarity restriction is linguistically questionable even for single-headed parsing, and even more so for multi-headed parsing.  So why not go straight to {\em non}-projective multi-headed parsing?  Mainly, because efficient algorithms often exist in the projective case, and these projective algorithms can be useful as an intermediate step in producing non-planar parses.  Since natural-language parses tend to be ``almost projective'' in practice (\cite{pitler}), one can use a fast projective parser as the first step in a coarse-to-fine or stacking architecture, in order to obtain preliminary edge scores that are supplied to a non-projective parser.  Another approach is 
``pseudo-projectivization,'' where we reversibly transform non-projective parses into a projective annotation style so that projective parsers can be used.
\noteJE{cite Pitler}}

@@

\begin{figure}[t!]
  \small
  \centering
  \includegraphics[width=0.7\textwidth, keepaspectratio=true]{figure/precision_recall.png}
  \caption{Rapid convergence to the direction mapping obtained on the largest dataset.  The direction mappings obtained on small datasets have high {\em precision} relative to the one obtained on the largest dataset.  Their {\em recall} grows as more link types are seen and directionalized.}\label{fig:convergence}
  \vspace{-6pt}
\end{figure}
